---
title: "Stock Screener"
output:
    flexdashboard::flex_dashboard:
        orientation: columns
        theme: 
          bootswatch: "lux"
          bg: "white"
          fg: "white"
          primary: "#18bc9c"
          secondary: "#18bc9c"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo    = FALSE,
    message = FALSE,
    warning = FALSE
)

library(shiny)
library(shinyjs)
library(plotly)
# library(bslib)
library(tidyverse)
library(timetk)
library(janitor)

```

``` {css}
.chart-title {
  background-color: black;
  color: white;
}

.chart-stage {
  background-color: black;
}

.section.sidebar {
  background-color: black;
}

.navbar.navbar-inverse {
  background-color: #18bc9c!important;
  box-shadow: 3px 3px 5px black;
}

.navbar-dark .navbar-brand, .navbar.navbar-inverse .navbar-brand {
  color:black;
}

.navbar.navbar-inverse ul.nav.navbar-nav>li.active>a {
  color:black;
}

.dashboard-column {
  background-color: black;
}

.section {
  background-color: black;
}

body {
  background-color:black;
}

```

```{r}

nasdaq_data_tbl    <- read_rds("raw_data/nasdaq_data_tbl.rds")
nasdaq_metrics_tbl <- read_rds("processed_data/nasdaq_metrics.rds")
nasdaq_index_tbl   <- read_rds("raw_data/nasdaq_index.rds") %>%
    clean_names()

```



# NASDAQ 4500+ Stock Investment

## Column {.sidebar}

<br>

__Learning Lab 65: Spark in R.__


#### What does the app do?

> Screens 4500 Stocks from the NASDAQ Exchange. 

<hr>

#### Filters

__Use filters__ to identify stocks for potential investment.

```{r}
useShinyjs(rmd = TRUE)

shiny::sliderInput(
    inputId = "market_cap", 
    label   = "Market Cap ($ Billions)", 
    min     = 0.5,
    value   = 1,
    max     = 100, 
    step    = 2
)

shiny::sliderInput(
    inputId = "max_sd", 
    label   = "Maximum Standard Deviation", 
    min     = 0.25,
    value   = 1,
    max     = 5, 
    step    = .25
)
    

    
actionButton(inputId = "apply", label = "Apply", icon = icon("play"))

actionButton(inputId = "reset", label = "Reset", icon = icon("sync"))


observeEvent(eventExpr = input$reset, handlerExpr = {
  
  updateSliderInput(
    inputId = "market_cap",
    value   = 1
  )
  
  updateSliderInput(
    inputId = "max_sd",
    value   = 1
  )
    
  shinyjs::delay(ms = 300, expr = {
      shinyjs::click(id = "apply")
  })
 
  
})


```

<hr>



> Based on the 1st Shiny App Project in Shiny Predictive Dashboards Course in the [5-Course R-Track Program](https://university.business-science.io/p/5-course-bundle-machine-learning-web-apps-time-series/?coupon_code=LEARNINGLABS)

Learn more at [Business Science](https://www.business-science.io/)


```{r}
# LOGIC

rv <- reactiveValues()

observeEvent(input$apply, {
  
    req(input$market_cap)
    req(input$max_sd)
    
    rv$nasdaq_metrics_screened_tbl <- nasdaq_metrics_tbl %>%
    
      inner_join(
          nasdaq_index_tbl %>% select(symbol, company, market_cap), 
          by = "symbol"
      ) %>%
      
      filter(market_cap > input$market_cap * 1e9) %>%
      
      arrange(-sd) %>%
      filter(
          sd < input$max_sd, 
          count > 365 * 5,
          last_date == max(last_date)
      ) %>%
      mutate(reward_metric = 2500*mean/sd) %>%
      mutate(desc = str_glue("
                             Symbol: {symbol}
                             Mean: {round(mean, 3)}
                             SD: {round(sd, 3)}
                             N: {count}
                             RWD: {round(reward_metric, 1)}"))
    
    
    n <- 9

    rv$best_symbols_tbl <- rv$nasdaq_metrics_screened_tbl %>%
        arrange(-reward_metric) %>%
        slice(1:n) 
    
    rv$best_symbols <- rv$best_symbols_tbl$symbol
    
    rv$stock_screen_data <- nasdaq_data_tbl %>%
        filter(symbol %in% rv$best_symbols) 
        
    
}, ignoreNULL = FALSE)
```


## Column 

<br>

### NASDAQ Stock Metrics

```{r}
output$plotly_1 <- renderPlotly({

    g <- rv$nasdaq_metrics_screened_tbl %>%
      ggplot(aes(log(sd), log(mean))) +
      geom_point(aes(text = desc, color = reward_metric), 
                 alpha = 0.5, shape = 21, size = 4) +
      geom_point(aes(text = desc), color = "#00ffcd",
                 alpha = 0.5, shape = 21, size = 4, 
                 data = rv$best_symbols_tbl) +
      geom_smooth() +
      scale_color_distiller(type = "div") +
      theme_minimal() +
      theme(
          panel.background = element_rect(fill = "black"),
          plot.background = element_rect(fill = "black"),
          text = element_text(colour = "white")
      ) 
  
  ggplotly(g)
})

plotlyOutput(outputId = "plotly_1")
```


## Column

<br>

### Best Stocks

```{r}
output$plotly_2 <- renderPlotly({

    facet_col <- 1

    if (length(input$products) > 3) facet_col <- 2

    if (length(input$products) > 8) facet_col <- 3

    g <- rv$stock_screen_data %>%
        left_join(
            rv$best_symbols_tbl %>% select(symbol, company)
        ) %>%
        group_by(symbol, company) %>%
        plot_time_series(date, adjusted, .smooth = TRUE, .facet_ncol = 3, .interactive = F) +
        geom_line(color = "white") +
        theme_minimal() +
        theme(
            panel.background = element_rect(fill = "black"),
            plot.background = element_rect(fill = "black"),
            text = element_text(colour = "white"),
            strip.text = element_text(colour = "white")
        ) +
        labs(title = "NASDAQ Financial Analysis")
    
    ggplotly(g)
})

plotlyOutput(outputId = "plotly_2")

```

